Ms 1

### 2018-01-22 ms1/ms1_display.Rmd
moved tables, updated tables

```{r pop_chars}
pop_chars = read_tsv('tables/new/study_pop_chars.tsv')

pop_chars = read_tsv('tables/new/study_pop_chars.tsv') %>%
  spread(key, value) %>%
  (function (df) {
    ns1 = names(df)
    ns2 = str_replace(ns1, '^n_(?!bene|cc)', 'pct_')
    rename(df, !!!setNames(as.list(ns1), ns2))
  }) %>%
  mutate_at(vars(matches('^pct_')), function(x) x / .$n_bene * 100) %>%
  gather('key', 'value', -year)

@@

```{r raw_drug_trends_table}
claims_by_abx = read_tsv('tables/new/claims_by_abx.tsv') %>%
  gather('abx', 'n', c(-year, -bene)) %>%
  mutate(cpkp=n/bene*1000)

claims_by_abx %>%
  mutate(cpkp=round(cpkp)) %>%
  select(year, abx, cpkp) %>%
  spread(year, cpkp) %>%
  arrange(desc(`2011`)) %>%
  kable(caption='Raw drug CPKP')
```

@@

abx_trends = read_tsv('tables/new/abx_models.tsv') %>%
  format_model()

@@

abx_trends %>%
  filter(antibiotic != 'metronidazole') %>%
  mutate(antibiotic=case_when(
    .$antibiotic == 'n_pde' ~ 'Overall use',
    .$antibiotic == 'n_pde_inapprop' ~ 'Inappropriate use',
    .$antibiotic == 'n_pde_approp' ~ 'Appropriate use',
    .$antibiotic == 'n_pde_nodx' ~ 'Indeterminate use',
    .$antibiotic == 'amoxclav' ~ 'amox/clav',
    .$antibiotic == 'tmpsmx' ~ 'TMP/SMX',
    TRUE ~ .$antibiotic)
  ) %>%
  # put the abx in order
  arrange(desc(estimate)) %>%
  mutate(antibiotic=fct_inorder(factor(antibiotic))) %>%
  mutate(antibiotic=fct_relevel(antibiotic, c('Overall use', 'Inappropriate use', 'Appropriate use', 'Indeterminate use'))) %>%
  mutate(antibiotic=fct_rev(antibiotic)) %>%
  # plot
  ggplot(aes(x=antibiotic, y=estimate, ymin=lower_ci, ymax=upper_ci)) +
  geom_bar(stat='identity', fill='white', color='black') +
  geom_errorbar(width=0.5) +
  coord_flip() +
  xlab('') +
  ylab('adjusted change in claims per beneficiary per year from 2011 to 2014 (%)') +
  scale_y_continuous(limits=c(-22, 33), breaks=c(-20, -10, 0, 10, 20, 30)) +
  theme_minimal() +
  theme(axis.title.x = element_text(size=12),
        axis.text = element_text(size=12))

@@

rxdx_table = read_tsv('tables/new/rxdx_counts.tsv') %>%
  left_join(denom, by='year') %>%
  mutate(cpkp=n_pdedx / bene * 1000)

@@

```{r prescribing_practice}
rxdx_models = read_tsv('tables/new/rxdx_models.tsv')

combined_table = rxdx_table %>%
  mutate(cpkp=round(n_pdedx / bene * 1000, 1)) %>%
  filter(year %in% c(2011, 2014)) %>%
  select(antibiotic, dx_cat, year, cpkp) %>%
  spread(year, cpkp) %>%
  right_join(rxdx_models, by=c('antibiotic', 'dx_cat')) %>%
  format_model() %>%
  select(dx_cat, antibiotic, `2011`, `2014`, change, p.value) %>%
  arrange(dx_cat, antibiotic)
```

@@

@@

```{r claims_by_demography}
subpop_table = read_tsv('tables/new/claims_by_subpop.tsv') %>%
  mutate(cpkp=round(n_pde/n_bene*1000)) %>%
  #filter(year %in% c(2011, 2014)) %>%
  select(subpop, year, cpkp) %>%
  spread(year, cpkp)

subpop_models = read_tsv('tables/new/subpop_models.tsv') %>%
  mutate_at(vars(estimate, lower_ci, upper_ci), est2pct) %>%
  mutate(pm=pmax(estimate-lower_ci, upper_ci-estimate)) %>%
  mutate(change=sprintf('%.1f (%.1f -- %.1f)', estimate, lower_ci, upper_ci)) %>%
  mutate(change2=sprintf('%.1f ± %.1f', estimate, pm)) %>%
  mutate(p.value=format_p(p_value)) %>%
  select(subpop, change2, p.value)

>>>>

```{r pop_chars}
pop_chars = read_tsv('tables/study_pop_chars.tsv')

pop_chars = read_tsv('tables/study_pop_chars.tsv') %>%
  spread(key, value) %>%
  (function (df) {
    ns1 = names(df)
    ns2 = str_replace(ns1, '^n_(?!bene|cc)', 'pct_')
    rename(df, !!!setNames(as.list(ns1), ns2))
  }) %>%
  mutate_at(vars(matches('^pct_')), function(x) x / .$n_bene * 100) %>%
  gather('key', 'value', -year)

@@

```{r raw_drug_trends_table}
claims_by_abx = read_tsv('tables/claims_by_abx.tsv') %>%
  gather('abx', 'n', c(-year, -bene)) %>%
  mutate(n=if_else(year == 2015 & abx %in% c('pde_approp', 'pde_inapprop', 'pde_nodx'),
                   as.integer(round(n * 4/3)),
                   n)) %>%
  mutate(cpkp=n/bene*1000)

claims_by_abx %>%
  mutate(cpkp=round(cpkp)) %>%
  select(year, abx, cpkp) %>%
  spread(year, cpkp) %>%
  arrange(desc(`2011`)) %>%
  kable(caption='Raw drug CPKP. 2015 values for abx-assoc. are projected.')
```

@@

abx_trends = read_tsv('tables/abx_models.tsv') %>%
  format_model()

@@

abx_trends %>%
  filter(antibiotic != 'metronidazole') %>%
  mutate(antibiotic=case_when(
    .$antibiotic == 'n_pde' ~ 'Overall use',
    .$antibiotic == 'n_pde_inapprop' ~ 'Inappropriate use',
    .$antibiotic == 'n_pde_approp' ~ 'Appropriate use',
    .$antibiotic == 'n_pde_nodx' ~ 'Indeterminate use',
    .$antibiotic == 'amoxclav' ~ 'amox/clav',
    .$antibiotic == 'tmpsmx' ~ 'TMP/SMX',
    TRUE ~ .$antibiotic)
  ) %>%
  # put the abx in order
  arrange(desc(estimate)) %>%
  mutate(antibiotic=fct_inorder(factor(antibiotic))) %>%
  mutate(antibiotic=fct_relevel(antibiotic, c('Overall use', 'Inappropriate use', 'Appropriate use', 'Indeterminate use'))) %>%
  mutate(antibiotic=fct_rev(antibiotic)) %>%
  # plot
  ggplot(aes(x=antibiotic, y=estimate, ymin=lower_ci, ymax=upper_ci)) +
  geom_bar(stat='identity', fill='white', color='black') +
  geom_errorbar(width=0.5) +
  coord_flip() +
  xlab('') +
  ylab('adjusted change in claims per beneficiary per year from 2011 to 2015 (%)') +
  scale_y_continuous(limits=c(-22, 33), breaks=c(-20, -10, 0, 10, 20, 30)) +
  theme_minimal() +
  theme(axis.title.x = element_text(size=12),
        axis.text = element_text(size=12))

@@

rxdx_table = read_tsv('tables/rxdx_counts.tsv') %>%
  left_join(denom, by='year') %>%
  mutate(cpkp=n_pdedx / bene * 1000) %>%
  mutate(cpkp=if_else(year==2015,
                      cpkp * 4/3,
                      cpkp))

@@

```{r prescribing_practice}
rxdx_models = read_tsv('tables/rxdx_models.tsv')

combined_table = rxdx_table %>%
  mutate(cpkp=round(cpkp, 1)) %>%
  filter(year %in% c(2011, 2015)) %>%
  select(antibiotic, dx_cat, year, cpkp) %>%
  spread(year, cpkp) %>%
  right_join(rxdx_models, by=c('antibiotic', 'dx_cat')) %>%
  format_model() %>%
  select(dx_cat, antibiotic, `2011`, `2015`, change, p.value) %>%
  arrange(dx_cat, antibiotic)
```

@@

## Any respiratory

```{r any_respiratory}
read_tsv('tables/rxdx_resp_counts.tsv') %>%
  left_join(denom, by='year') %>%
  mutate(n_pdedx=if_else(year==2015, n_pdedx * 4/3, as.numeric(n_pdedx))) %>%
  mutate(cpkp=round(n_pdedx / bene * 1000, 1)) %>%
  filter(year %in% c(2011, 2015)) %>%
  select(antibiotic, year, cpkp) %>%
  spread(year, cpkp) %>%
  mutate(change=`2015`-`2011`) %>%
  kable(caption='Claims per 1,000 beneficiaries of each drug in association with any of the considered respiratory diagnoses')
```

@@

```{r claims_by_demography}
subpop_table = read_tsv('tables/claims_by_subpop.tsv') %>%
  mutate(cpkp=round(n_pde/n_bene*1000)) %>%
  filter(year %in% c(2011, 2015)) %>%
  select(subpop, year, cpkp) %>%
  spread(year, cpkp)

subpop_models = read_tsv('tables/subpop_models.tsv') %>%
  mutate_at(vars(estimate, lower_ci, upper_ci), est2pct) %>%
  mutate(pm=pmax(estimate-lower_ci, upper_ci-estimate)) %>%
  mutate(change=sprintf('%.1f ± %.1f', estimate, ceiling_at(pm, 1))) %>%
  mutate(p.value=format_p(p_value)) %>%
  select(subpop, change, p.value)
